---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pharmapkgs

<!-- badges: start -->
<!-- badges: end -->

The goal of `{pharmapkgs}` is to facilitate the interfacing with CRAN-like
repositories of validated packages with risk metrics.

## Installation

``` r
# install.packages("devtools")
devtools::install_github("pharmaR/pharmapkgs")
```

## Bare bones demo

All available packages from local repository.

```{r}
library(pharmapkgs)

# A local repository, bundled with pharmapkgs.
(repo <- bundled_repos("ubuntu-22.04"))

# No filtering.
all_pkgs <-
  available.packages(contriburl = repo,
                     fields = risk_fields(repo)) |>
  tibble::as_tibble()

dplyr::glimpse(all_pkgs)
```

Packages filtered using `{riskmetrics}` criteria.

```{r}
# Fancy criteria. 
my_filters <- risk_filter(ReverseDependencies < 0.5, HasNews == "1", RemoteChecks > 0.9)

# Validated packages.
val_pkgs <-
  available.packages(contriburl = repo,
                     fields = risk_fields(repo),
                     filters = my_filters) |>
  tibble::as_tibble()

dplyr::glimpse(val_pkgs)
```

Currently, not working, `pak::pkg_install()` is not downloading packages
based on the DownloadURL field from the local repository.

```{r}
if ("munsell" %in% rownames(installed.packages()))
  pak::pkg_remove("munsell")

pak::cache_clean()
options(repos = repo)
getOption("repos")

# Install one of the validated packages with pak.
istats <- pak::pkg_install("standard::munsell") |>
  tibble::as_tibble()
  
dplyr::glimpse(istats)

istats$sources

istats$ref
```

## Not working

Filtering through `options()` does not seem to work.

```{r}
# Not working.
options(fields = risk_fields(repo),
        available_package_filters = my_filters)
available.packages(contriburl = repo) |>
  tibble::as_tibble() |>
  dplyr::glimpse()
```

## TODO

- Modify installed package DESCRIPTION post-installation to include metrics
- "report" that uses metrics/logs to populate a template
