---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

options(
  cli.ansi = FALSE,
  cli.dynamic = FALSE
)
```

# pharmapkgs

<!-- badges: start -->
<!-- badges: end -->

The goal of `{pharmapkgs}` is to facilitate the interfacing with CRAN-like
repositories of validated packages with risk metrics.

## Installation

_using `devtools`_

```r
# install.packages("devtools")
devtools::install_github("pharmaR/pharmapkgs")
```

_using `pak`_

```r
# install.packages("pak")
pak::pkg_install("github::pharmaR/pharmapkgs")
```

## Bare Bones Demo

All available packages from local repository.

```{r}
library(pharmapkgs)

# local snapshot, bundled with pharmapkgs
repo <- bundled_repos("ubuntu-22.04")

available.packages(repos = repo, fields = risk_fields(repo)) |>
  tibble::as_tibble()
```

Packages filtered using `{riskmetrics}` criteria.

```{r}
# Fancy criteria.
my_filters <- risk_filter(
  ReverseDependencies < 0.5,
  HasNews == "1",
  RemoteChecks > 0.9
)

# Apply filter when inspecting packages
tibble::as_tibble(available.packages(
  repos = repo,
  fields = risk_fields(repo),
  filters = my_filters
))
```

## Filtered Available Packages Workflow

Configure a session to leverage a bundled repo.

```{r}
repo <- bundled_repos("ubuntu-22.04")
options(
  # importantly, repo is called CRAN such that pak doesn't insert a CRAN mirror
  # awaiting feature r-lib/pak#637
  repos = c(CRAN = repo)
)

nrow(available.packages())
```

We can provide a filter based on various risk criteria, that will allow `pak` to
leverage the same internal mechanisms for fetching packages and ensuring, at the
time of download, that packages adhere to the filters that we specify.

Now apply a filter and observe a reduced subset of available packages.

```{r}
options(
  available_packages_filters = risk_filter(
    RemoteChecks > 0.9,
    HasNews == "1"
  )
)

nrow(available.packages())
```

Install a package, and confirm that the package was pulled from the bundled
download location, ensuring that the downloaded version of the package is the
same that was used to derive the risk metrics.

```{r}
pak::cache_clean()
pkg <- "colorspace"

if (pkg %in% rownames(installed.packages()))
  pak::pkg_remove(pkg)

install_stats <- pak::pkg_install(pkg)
install_stats$sources
```
