


## Unit Test Report

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, results = "asis")
library(dplyr)

SummariseResults <- function(res) {
  res %>% summarise_if(is.numeric, sum) %>% knitr::kable()
}
WriteResults <- function(res) {
  purrr::pwalk(list(res$file, res$Categories), WriteFileResults)
}
WriteFileResults <- function(file, categories, ...) {
  cat("###", file, "\n")
  purrr::pwalk(list(categories$context, categories$Results), WriteCategoryResults)
}
WriteCategoryResults <- function(category, tests, ...) {
  cat("####", category, "\n")
  print(knitr::kable(tests))
}
path0 <- here::here()

if(!require(KinGUI)) devtools::load_all(path0)
library(devtools)
#library(golem)
```

```{r include=FALSE}
devtools::test() ## This block is needed due to produce the correct report. Donot remove it. 
```



```{r GenerateResults}
file_lists <- list.files(paste0(path0,"/tests/testthat/"))
if("_snaps" %in% file_lists) {file_lists <- file_lists[file_lists!="_snaps"]}
testResultsRaw_list <- lapply(file_lists,function(x)testthat::test_file(paste0(path0,"/tests/testthat/",x), reporter = testthat::ListReporter))

testResultsIndividual_list <- lapply(testResultsRaw_list,function(x) x%>%
  as_tibble() %>%
  rename(Test = test) %>%
  group_by(file, context, Test) %>%
  summarise(NumTests = first(nb),
            Passed   = sum(passed),
            Failed   = sum(failed),
            Warnings = sum(warning),
            Errors   = sum(as.numeric(error)),
            Skipped  = sum(as.numeric(skipped)),
            .groups = "drop"))
testResultsIndividual<- plyr::ldply(testResultsIndividual_list)##%>%dplyr::select(-context)
testResultsNested <- testResultsIndividual %>%
  nest_by(file, context, .key = "Results") %>%
  nest_by(file, .key = "Categories")
```

## Unite TesSummary
```{r WriteSummary}
SummariseResults(testResultsIndividual)
```

## Unit Test Details
```{r WriteResults}
WriteResults(testResultsNested)
## knitr::kable(testResultsIndividual)
```



## System Test Protocol 
## List of Test Cases 
## System Test Execution Report

> ðŸ“˜ Info: WIP
> 
> This is merely a starting point for the full validation report. 

Table of contents:

- [ ] Risk metrics report
- [ ] Risk score / characterization
- [ ] Unit Test Report
- [ ] System Test Protocol
- [ ] Test Cases Definition 
- [ ] Test Cases Execution Report

Styles: 

- [ ] R Validation Hub logo?
- [ ] Style of word document? 


> ðŸ‘ Success
>
> Vitae reprehenderit at aliquid error voluptates eum dignissimos.

# References

- White Paper
- https://github.com/pharmaR/riskassessment/tree/master/inst/report_downloads
